Global Life Expectancy: Unraveling Health and Economic Determinants (2015-2020)\thanks{Code and data are available at: \url{https://github.com/wendyhuan/lifeexpectancy}.}

### 2024-12-03 paper/paper.tex
initial

\textbf{?@fig-cleaned} shows the average of life expectancy under male,
female, 6 different regions and 4 income groups.

@@

The outcome variable is \textbf{\texttt{Life\ Expendency}}. This is the
primary dependent variable that the model is designed to predict. It
represents the average number of years a person is expected to live,
under the condition that current mortality conditions persist. The model
seeks to identify the variables affecting this average.

@@

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

@@

Our results are summarized in Table~\ref{tbl-modelresults}.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  check different continent has its different life expectancy.
\item
  compare the develop country with
\item
  check the shcooling year of develop countries to developing country,
  showing a relationship between shcooling with the life expenctancy.
\item
\end{enumerate}

@@

\subsection{First discussion point}\label{sec-first-point}

@@

>>>>

shows the average of life expectancy under male, female, 6 different
regions and 4 income groups.

@@

The outcome variable is \textbf{Life Expectancy}. This is the primary
dependent variable that the model is designed to predict. It represents
the average number of years a person is expected to live, under the
condition that current mortality conditions persist. The model seeks to
identify the variables affecting this average.

@@

The GAM was chosen for this analysis due to its ability to capture
non-linear relationships between predictors and the outcome variable,
which is essential when dealing with categorical predictors like income
group and the

@@

\subsection{Overview of model results}\label{overview-of-model-results}

Our results are summarized in Table~\ref{tbl-modelresults}. We are
primarily interest in the

\subsection{Multiple linear regression
results}\label{multiple-linear-regression-results}

@@

\subsection{Insights into different
gender}\label{insights-into-different-gender}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2245}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.3605}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0476}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0748}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1088}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0884}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0952}}@{}}

\caption{\label{tbl-cleaned_leab}Life expectancy over countries and
years}

\tabularnewline

\caption{Life Expectancy over countries and years}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Indicator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Country
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Period
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Gender
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Life Expectancy
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Income\_Group
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Region
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Indicator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Country
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Period
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Gender
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Life Expectancy
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Income\_Group
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Region
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Life expectancy at birth (years) & Afghanistan & 2020 & Male & 59.3 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2020 & Both sexes &
60.5 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2020 & Female & 61.7 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2019 & Male & 60.0 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2019 & Both sexes &
61.2 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2019 & Female & 62.5 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2018 & Male & 59.0 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2018 & Both sexes &
60.5 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2018 & Female & 62.1 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2017 & Male & 59.8 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2017 & Both sexes &
60.9 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2017 & Female & 62.1 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2016 & Male & 59.2 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2016 & Both sexes &
60.4 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2016 & Female & 61.7 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2015 & Male & 59.3 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2015 & Both sexes &
60.3 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2015 & Female & 61.5 &
lower\_income & Asia \\
Life expectancy at birth (years) & Albania & 2020 & Male & 74.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2020 & Both sexes & 76.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2020 & Female & 79.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2019 & Male & 76.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2019 & Both sexes & 77.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2019 & Female & 79.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2018 & Male & 76.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2018 & Both sexes & 77.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2018 & Female & 79.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2017 & Male & 76.1 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2017 & Both sexes & 77.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2017 & Female & 79.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2016 & Male & 76.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2016 & Both sexes & 77.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2016 & Female & 79.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2015 & Male & 76.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2015 & Both sexes & 77.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2015 & Female & 79.6 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Algeria & 2020 & Male & 73.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2020 & Both sexes & 74.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2020 & Female & 75.2 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2019 & Male & 76.2 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2019 & Both sexes & 76.5 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2019 & Female & 77.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2018 & Male & 76.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2018 & Both sexes & 76.4 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2018 & Female & 77.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2017 & Male & 76.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2017 & Both sexes & 76.4 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2017 & Female & 77.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2016 & Male & 75.9 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2016 & Both sexes & 76.3 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2016 & Female & 76.8 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2015 & Male & 75.8 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2015 & Both sexes & 76.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2015 & Female & 76.6 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2020 & Male & 60.4 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2020 & Both sexes & 62.6 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2020 & Female & 64.9 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2019 & Male & 60.3 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2019 & Both sexes & 62.5 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2019 & Female & 64.7 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2018 & Male & 60.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2018 & Both sexes & 62.3 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2018 & Female & 64.5 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2017 & Male & 59.8 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2017 & Both sexes & 62.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2017 & Female & 64.3 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2016 & Male & 59.5 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2016 & Both sexes & 61.8 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2016 & Female & 64.2 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2015 & Male & 59.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2015 & Both sexes & 61.6 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2015 & Female & 64.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Male &
75.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Both
sexes & 77.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Female &
79.4 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Male &
74.0 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Both
sexes & 75.7 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Female &
77.1 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Male &
74.0 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Both
sexes & 75.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Female &
77.0 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Male &
73.9 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Both
sexes & 75.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Female &
77.0 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Male &
73.8 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Both
sexes & 75.5 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Female &
77.1 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Male &
73.8 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Both
sexes & 75.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Female &
77.2 & high\_income & North America \\
Life expectancy at birth (years) & Argentina & 2020 & Male & 73.1 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2020 & Both sexes & 76.2
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2020 & Female & 79.4 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2019 & Male & 74.0 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2019 & Both sexes & 77.0
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2019 & Female & 79.9 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2018 & Male & 73.7 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2018 & Both sexes & 76.9
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2018 & Female & 79.9 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2017 & Male & 73.6 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2017 & Both sexes & 76.6
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2017 & Female & 79.6 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2016 & Male & 73.0 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2016 & Both sexes & 76.1
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2016 & Female & 79.2 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2015 & Male & 73.3 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2015 & Both sexes & 76.5
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2015 & Female & 79.6 &
upper\_middle & South America \\
Life expectancy at birth (years) & Armenia & 2020 & Male & 62.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2020 & Both sexes & 69.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2020 & Female & 76.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2019 & Male & 70.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2019 & Both sexes & 75.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2019 & Female & 79.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2018 & Male & 71.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2018 & Both sexes & 75.6 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2018 & Female & 79.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2017 & Male & 70.6 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2017 & Both sexes & 75.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2017 & Female & 79.1 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2016 & Male & 69.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2016 & Both sexes & 74.4 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2016 & Female & 78.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2015 & Male & 69.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2015 & Both sexes & 74.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2015 & Female & 78.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Australia & 2020 & Male & 81.5 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2020 & Both sexes & 83.4
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2020 & Female & 85.2 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2019 & Male & 80.7 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2019 & Both sexes & 82.6
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2019 & Female & 84.6 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2018 & Male & 81.2 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2018 & Both sexes & 83.0
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2018 & Female & 84.9 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2017 & Male & 80.8 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2017 & Both sexes & 82.7
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2017 & Female & 84.5 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2016 & Male & 80.7 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2016 & Both sexes & 82.6
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2016 & Female & 84.5 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2015 & Male & 80.4 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2015 & Both sexes & 82.3
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2015 & Female & 84.2 &
high\_income & Oceania \\
Life expectancy at birth (years) & Austria & 2020 & Male & 78.8 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2020 & Both sexes & 81.1 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2020 & Female & 83.3 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2019 & Male & 79.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2019 & Both sexes & 81.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2019 & Female & 83.8 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2018 & Male & 79.2 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2018 & Both sexes & 81.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2018 & Female & 83.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2017 & Male & 79.2 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2017 & Both sexes & 81.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2017 & Female & 83.5 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2016 & Male & 79.1 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2016 & Both sexes & 81.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2016 & Female & 83.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2015 & Male & 78.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2015 & Both sexes & 81.0 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2015 & Female & 83.3 &
high\_income & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2020 & Male & 67.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2020 & Both sexes & 71.4
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2020 & Female & 75.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2019 & Male & 73.4 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2019 & Both sexes & 75.8
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2019 & Female & 78.1 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2018 & Male & 72.6 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2018 & Both sexes & 75.1
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2018 & Female & 77.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2017 & Male & 72.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2017 & Both sexes & 74.6
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2017 & Female & 76.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2016 & Male & 71.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2016 & Both sexes & 74.0
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2016 & Female & 76.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2015 & Male & 71.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2015 & Both sexes & 73.6
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2015 & Female & 75.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Bahamas & 2020 & Male & 69.2 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2020 & Both sexes & 72.6 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2020 & Female & 76.0 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2019 & Male & 68.1 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2019 & Both sexes & 70.7 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2019 & Female & 73.3 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2018 & Male & 70.2 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2018 & Both sexes & 73.4 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2018 & Female & 76.5 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2017 & Male & 70.0 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2017 & Both sexes & 73.2 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2017 & Female & 76.3 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2016 & Male & 69.7 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2016 & Both sexes & 72.9 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2016 & Female & 76.1 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2015 & Male & 69.8 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2015 & Both sexes & 72.9 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2015 & Female & 76.0 &
high\_income & North America \\
Life expectancy at birth (years) & Bahrain & 2020 & Male & 73.6 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2020 & Both sexes & 74.9 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2020 & Female & 76.8 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2019 & Male & 75.4 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2019 & Both sexes & 76.0 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2019 & Female & 76.9 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2018 & Male & 75.1 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2018 & Both sexes & 75.9 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2018 & Female & 77.0 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2017 & Male & 74.9 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2017 & Both sexes & 75.7 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2017 & Female & 76.8 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2016 & Male & 75.0 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2016 & Both sexes & 75.7 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2016 & Female & 76.5 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2015 & Male & 75.2 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2015 & Both sexes & 75.8 &
high\_income & Asia \\
Life expectancy at birth (years) & Bahrain & 2015 & Female & 76.5 &
high\_income & Asia \\
Life expectancy at birth (years) & Bangladesh & 2020 & Male & 71.7 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2020 & Both sexes & 73.3
& lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2020 & Female & 75.0 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2019 & Male & 72.6 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2019 & Both sexes & 73.9
& lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2019 & Female & 75.3 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2018 & Male & 72.4 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2018 & Both sexes & 73.7
& lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2018 & Female & 75.0 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2017 & Male & 72.1 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2017 & Both sexes & 73.4
& lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2017 & Female & 74.7 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2016 & Male & 72.3 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2016 & Both sexes & 73.4
& lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2016 & Female & 74.6 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2015 & Male & 72.1 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2015 & Both sexes & 73.2
& lower\_middle & Asia \\
Life expectancy at birth (years) & Bangladesh & 2015 & Female & 74.3 &
lower\_middle & Asia \\
Life expectancy at birth (years) & Barbados & 2020 & Male & 75.1 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2020 & Both sexes & 76.9 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2020 & Female & 78.6 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2019 & Male & 74.3 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2019 & Both sexes & 76.0 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2019 & Female & 77.6 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2018 & Male & 74.9 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2018 & Both sexes & 76.3 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2018 & Female & 77.5 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2017 & Male & 75.1 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2017 & Both sexes & 76.3 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2017 & Female & 77.5 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2016 & Male & 75.1 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2016 & Both sexes & 76.3 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2016 & Female & 77.4 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2015 & Male & 75.1 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2015 & Both sexes & 76.3 &
high\_income & North America \\
Life expectancy at birth (years) & Barbados & 2015 & Female & 77.4 &
high\_income & North America \\
Life expectancy at birth (years) & Belarus & 2020 & Male & 67.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2020 & Both sexes & 73.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2020 & Female & 78.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2019 & Male & 69.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2019 & Both sexes & 74.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2019 & Female & 79.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2018 & Male & 69.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2018 & Both sexes & 74.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2018 & Female & 79.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2017 & Male & 69.1 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2017 & Both sexes & 74.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2017 & Female & 79.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2016 & Male & 68.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2016 & Both sexes & 73.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2016 & Female & 78.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2015 & Male & 68.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2015 & Both sexes & 73.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belarus & 2015 & Female & 78.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Belgium & 2020 & Male & 78.7 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2020 & Both sexes & 80.8 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2020 & Female & 82.9 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2019 & Male & 79.5 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2019 & Both sexes & 81.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2019 & Female & 83.7 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2018 & Male & 79.1 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2018 & Both sexes & 81.2 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2018 & Female & 83.3 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2017 & Male & 78.9 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2017 & Both sexes & 81.2 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2017 & Female & 83.3 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2016 & Male & 78.7 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2016 & Both sexes & 81.1 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2016 & Female & 83.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2015 & Male & 78.5 &
high\_income & Europe \\
Life expectancy at birth (years) & Belgium & 2015 & Both sexes & 80.7 &
high\_income & Europe \\
